---
title: Polish
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Polish}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mRclwhip)
```

The idea behind ```mRclwhip::polish()``` is to create a more 'complete product' than what is returned
from ```broom::tidy()```, for example.  

<br> <br>

The function can either return a ```flextable::flextable()``` object if the argument
```.flextable = TRUE```. 
<br>
Or, if the argument ```.flextable = FALSE```, then a list with two objects is returned where the first
object in the list is a dataframe of the polished results that can be further manipulated.  
<br>
The second object in the list is a vector of row numbers that can then be passed into
```flextable::padding()``` (after passing the dataframe into ```mRclwhip::format_flextable()``` of course)
to pad the rows with factor levels.  
<br>
The example at the end will provide further clarification.


### Example using ```coxph()```
```{r}
mockstudy <- arsenal::mockstudy
coxph_res <- survival::coxph(survival::Surv(fu.time, fu.stat) ~ race + sex + bmi, data = mockstudy)

Hmisc::label(mockstudy$sex) <- "Gender"

coxph_res %>%
  polish(
    .header1 = list(values = c("", "HR (95% CI)")),
    exponentiate = T
  )
```
  

### Example using ```lm()```
```{r}
mtcars <- mtcars %>%
  dplyr::mutate_at(dplyr::vars(gear, am, carb), as.character)

mtcars <- Hmisc::upData(
  mtcars,
  labels = c(mpg = "MPG",
             hp = "HP",
             gear = "# of gears",
             am = "Automatic",
             wt = "Weight",
             carb = "Carb"
             ),
  print = F
  )

lm_res <- lm(mpg ~ hp + gear + am + wt + carb, data = mtcars)

lm_res %>%
  polish(
    .header1 = list(values = c("", "Estimate (95% CI)"))
  )
```
  

### Example using ```lm()``` with labels argument used correctly
```{r}
mtcars <- mtcars %>%
  dplyr::mutate_at(dplyr::vars(gear, am, carb), as.character)

labs <- c(hp = "HP",
          gear = "# of gears",
          am = "Automatic",
          wt = "Weight",
          carb = "Carb"
          )

lm_res <- lm(mpg ~ hp + gear + am + wt + carb, data = mtcars)

lm_res %>%
  polish(
    .header1 = list(values = c("", "Estimate (95% CI)")),
    .labels = labs
  )
```
  

### Example using ```lm()``` with labels argument used incorrectly
```{r, error = T}
mtcars <- mtcars %>%
  dplyr::mutate_at(dplyr::vars(gear, am, carb), as.character)

labs <- c(mpg = "MPG",
          hp = "HP",
          gear = "# of gears",
          am = "Automatic",
          wt = "Weight",
          carb = "Carb"
)

lm_res <- lm(mpg ~ hp + gear + am + wt + carb, data = mtcars)

lm_res %>%
  polish(
    .header1 = list(values = c("", "Estimate (95% CI)")),
    .labels = labs
  )
```
  

### Example using ```.flextable = FALSE``` where a list with a dataframe and a vector of row numbers is returned
```{r}
mtcars <- mtcars %>%
  dplyr::mutate_at(dplyr::vars(gear, am, carb), as.character)

mtcars <- Hmisc::upData(
  mtcars,
  labels = c(mpg = "MPG",
             hp = "HP",
             gear = "# of gears",
             am = "Automatic",
             wt = "Weight",
             carb = "Carb"
             ),
  print = F
  )

lm_res <- lm(mpg ~ hp + gear + am + wt + carb, data = mtcars)

res <- lm_res %>%
  polish(
    .flextable = FALSE
  )

res
```
  

Returning the dataframe allows further manipulation if desired. The row numbers returned for the
rows with factor levels can then be used in ```flextable::padding()``` to add padding
```{r}
res[[1]] %>% 
  mRclwhip::format_flextable(header1 = list(values = c("", "Estimate (95% CI)"))) %>% 
  flextable::padding(i = res[[2]], j = 1, padding.left = 25)
```
